Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-19 paper/main.tex
Expand and format data citations

% cut anno
1. Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
locations, and temporal progression in the motion picture "Forrest Gump".
\emph{F1000Research}
\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
(2016)

% speech anno
2. Häusler, C. O. \& Hanke M. \emph{OSF}
\href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
(2020).

% audio-description
3. Hanke, M., Baumgartner, F. J., Ibe, P., Kaule, F. R., Pollmann, S., Speck,
O., Zinke, W. \& Stadler, J. \emph{OpenNEURO}
\href{https://openneuro.org/datasets/ds000113}{ds000113} (2014). \todo{4
datasets \& using authors/year of the audio-description}

>>>>

\begin{itemize}
% cut anno
\item Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
locations, and temporal progression in the motion picture "Forrest Gump".
\emph{F1000Research}
\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
(2016)

% speech anno
\item Häusler, C. O. \& Hanke M. \emph{OSF}
\href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
(2020).

% audio-description
\item Hanke, M., Baumgartner, F.~J., Ibe, P., Kaule, F.~R., Pollmann, S., Speck, O.,
  Zinke, W., \& Stadler, J. \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113}{ds000113} (2014)

\item Sengupta, A., Kaule, F. R., Guntupalli, J. S., Hoffmann, M. B., Häusler, C., Stadler, J. \& Hanke, M.
  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113c}{ds000113c} (2016).

\item Hanke, M., Adelhöfer, N., Kottke, D., Iacovella, V., Sengupta, A., Kaule, F.~R., Nigbur, R., Waite, A.~Q.,
  Baumgartner, F.~J. \& Stadler, J. (2016).
  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113d}{ds000113d} (2016).
\end{itemize}
